Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex
v\dual to f\dual
final micro changes

We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.

@@

We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
The latter is directly inspired from the case of a disk treated in~\cite{GarverMcConville}, while the former is obtained by duality as was already observed in the case of a disk in~\cite{MannevillePilaud-accordion}.
In the general case of arbitrary orientable surfaces, the correspondence between accordions and slaloms requires a little more attention and is treated in Section~\ref{subsec:accordionsVSSlaloms}.

@@

Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
%
%\begin{definition}
%A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
%Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
%\end{definition}
%
%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-curve can cross an external $B$-curve.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.

@@

The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.

@@

Case 1: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
Consider the connected component of~$f\setminus\alpha$ that does not contain~$f\dual$.
The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that share a common endpoint with~$a$.
Let~$u,v$ be the endpoints of~$c$.
Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both endpoints of~$\delta$.

@@

\begin{proof}
The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
 Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
\end{proof}

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface_{\bar Q}$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
\begin{alignat*}{2}
& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
\text{and} \qquad & \Ers{\alpha} = [v\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [v\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
\end{alignat*}
placed as follows:

\centerline{
\begin{tikzpicture}[
	scale=1.5,
	thick,
	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=1.5pt}
	]
	\node[roundNode, label={[label distance=-3pt]left:{$s(\alpha)$}}] (s) at (-1,0) {};
	\node[roundNode, label={[label distance=-3pt]right:{$t(\alpha)$}}] (t) at (1,0) {};
	\node[roundNode, fill=green, label={[label distance=-3pt]above:{$\green v(\alpha)$}}] (v) at (0,1) {};
	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red v\dual(\alpha)$}}] (vd) at (0,-1) {};
	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left, outer sep=-3pt] {$\green \Enrs{\alpha}$};
	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right, outer sep=-3pt] {$\green \Enrt{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left, outer sep=-3pt] {$\red \Ers{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right, outer sep=-3pt] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

@@

The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.

@@

\enlargethispage{.2cm}
We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have no punctures and
\begin{itemize}
\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $2$ boundary components and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.

@@

For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
\begin{itemize}
\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise (resp.~clockwise) direction.
\end{itemize}
Examples are illustrated in \fref{fig:peakDeep}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{peakDeep}}
	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
	\label{fig:peakDeep}
\end{figure}

@@

\begin{remark}
 We note that, since the walks~$\mu$ and~$\nu$ are non-kissing, if~$\mu_\star$ leaves~$\sigma$ on both sides, then is enters and exits~$\sigma$ in the same direction, so that Definition~\ref{def:orderForWalks} is coherent.
\end{remark}

\begin{remark}
\label{rem:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$f\dual$,~$v\in f$, between two edges of~$\dissection\dual$).
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$f\dual$) than~$\delta$ does.
These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angles of~$\dissection$ and~$\dissection\dual$ corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

@@

\begin{proof}[Combinatorial proof]
By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+p$, where~$p$ is the number of infinite straight walks (i.e. the number of primitive oriented cycles in~$Q$).

@@

Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.27]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the statement for one of them.
The following definition from \cite[Def.~2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.

@@

\begin{lemma}
\label{lem:walksThroughcycles}
For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$ (i.e. the walk is not an infinite straight walk).
\end{lemma}

@@

The following result extends \cite[Prop.~2.26]{PaluPilaudPlamondon} to the case of locally gentle algebras.

@@

\begin{proof}
The proof of \cite[Prop.~2.26]{PaluPilaudPlamondon} applies here to show that each walk in the non-kissing facet~$F$ has at most one distinguished arrow in each direction.
Lemma~\ref{lem:ExistenceOfDistinguishedArrows} therefore shows the first two points.
Finally, Lemma~\ref{lem:walksThroughcycles} shows the last point.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop:purity}.]
The proof follows that of~\cite[Cor.~2.27]{PaluPilaudPlamondon}.
Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
Moreover, the infinite straight walks are just the primitive oriented cycles in~$\bar Q$.

@@

A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
We state the following results, which generalize \cite[Prop.~2.31 \& Cor.~2.33]{PaluPilaudPlamondon}, whose proofs apply without change.

@@

\begin{definition}
Let~$V \eqdef \{a_1, \dots, a_m\}$ be a multiset of vertices of~$Q_0$. We denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined~by:
\[
\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{a_i} = \sum_{a \in Q_0} |\set{i \in [m]}{a_i = a}| \, \b{e}_a.
\]
For a string~$\sigma$ of~$\bar Q$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
\end{definition}

@@

\begin{proposition}
\label{prop:gVectorsSurface}
For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
\begin{enumerate}[(i)]
\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(a)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(a)$ of~$\dissection$. Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
We note that some crossings are neither positive nor negative.
\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$. Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
We note that, in this case, each crossing is either positive or negative.
\end{enumerate}
\end{proposition}

@@

\begin{proof}
For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.
\end{proof}

>>>>

\enlargethispage{.2cm}
We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.

@@

\enlargethispage{.1cm}
We now temporarily switch topic and present the accordion complex and the slalom complex of a pair of dual dissections of an orientable surface.
The latter is directly inspired from the case of a disk treated in~\cite{GarverMcConville}, while the former is obtained by duality as was already observed in the case of a disk in~\cite{MannevillePilaud-accordion}.
In the general case of arbitrary orientable surfaces, the correspondence between accordions and slaloms requires a little more attention and is treated in Section~\ref{subsec:accordionsVSSlaloms}.

@@

\enlargethispage{.1cm}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points on the boundary of~$\surface$.
%
%\begin{definition}
%A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
%Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
%\end{definition}
%
%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-curve can cross an external $B$-curve.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.

@@

\enlargethispage{.3cm}
The following definition generalizes the one from~\cite{GarverMcConville} for the case where~$\bar\surface$ is a disk.

@@

Case 1: The curve~$\alpha$ consecutively crosses two edges~$a$ and~$b$ of~$\dissection$ that do not share a common endpoint.
Let~$f$ be the face of~$\dissection$ that contains the segment of~$\alpha$ between~$a$ and~$b$.
Consider the connected component of~$f\setminus\alpha$ that does not contain~$f\dual$.
The boundary of this component contains an edge~$c \in \dissection \setminus \{a\}$ that shares a common endpoint with~$a$.
Let~$u,v$ be the endpoints~of~$c$.
Then~$\alpha$ cuts the cells $u\dual,v\dual$ glued along~$c\dual$ into two connected components, one containing both~endpoints~of~$\delta$.

@@

\begin{proof}
The duality provides a bijection~$a\in (Q_\dissection)_0\mapsto a\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
\end{proof}

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface_{\bar Q}$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
\begin{alignat*}{2}
& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
\text{and} \qquad & \Ers{\alpha} = [f\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [f\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
\end{alignat*}
placed as follows:

\centerline{
\begin{tikzpicture}[
	scale=1.5,
	thick,
	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=1.5pt}
	]
	\node[roundNode, label={[label distance=-3pt]left:{$s(\alpha)$}}] (s) at (-1,0) {};
	\node[roundNode, label={[label distance=-3pt]right:{$t(\alpha)$}}] (t) at (1,0) {};
	\node[roundNode, fill=green, label={[label distance=-3pt]above:{$\green v(\alpha)$}}] (v) at (0,1) {};
	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red f\dual(\alpha)$}}] (vd) at (0,-1) {};
	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left, outer sep=-3pt] {$\green \Enrs{\alpha}$};
	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right, outer sep=-3pt] {$\green \Enrt{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left, outer sep=-3pt] {$\red \Ers{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right, outer sep=-3pt] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

@@

\enlargethispage{-.4cm}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows~$\surface_{\bar Q}$ with two disjoint sets~$V_{\bar Q}$ and~${{V\dual}\!\!_{\bar Q}}$ of marked points and two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection\dual\!\!_{\bar Q}}$ defined as follows.

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have no punctures and
\begin{itemize}
\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $2$ boundary components and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.

@@

%For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
\begin{itemize}
\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ until it reaches the following blossom vertex along the boundary of~$\surface$ while keeping the boundary of~$\surface$ on the right,
\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise (resp.~clockwise) direction.
\end{itemize}
Examples are illustrated in \fref{fig:peakDeep}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{peakDeep}}
	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
	\label{fig:peakDeep}
\end{figure}

@@

\begin{remark}
Since the walks~$\mu$ and~$\nu$ are non-kissing, if~$\mu_\star$ leaves~$\sigma$ on both sides, then is enters and exits~$\sigma$ in the same direction, so that Definition~\ref{def:orderForWalks} is coherent.
\end{remark}

\begin{remark}
\label{rem:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two edges of~$\dissection$ (resp.~at a point~$f\dual$ between two edges of~$\dissection\dual$).
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$f\dual$) than~$\delta$ does.
These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angles of~$\dissection$ and~$\dissection\dual$ corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

@@

\begin{proof}[Combinatorial proof]
By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+p$, where~$p$ is the number of infinite straight walks (\ie the number of primitive oriented cycles in~$Q$).

@@

Note that Proposition \ref{prop:purity} was proved for~$\NKC$ in \cite[Cor.~2.29]{PaluPilaudPlamondon} in the case where~$kQ/I$ is finite-dimensional.
Note also that, by Theorem \ref{thm:complexesCoincide} above,~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$ coincide, so it suffices to prove the statement for one of them.
The following definition from \cite[Def.~2.25]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.

@@

\begin{lemma}
\label{lem:walksThroughcycles}
For any oriented cycle~$c$ in~$Q$ with~$c, c^2\notin I$, any maximal non-kissing face contains a walk of the form~$\sigma c^{\varepsilon\infty}$, for some~$\varepsilon\in\{\pm1\}$ and some substring~$\sigma$ distinct from~$^{\varepsilon\infty}c$ (\ie the walk is not an infinite straight walk).
\end{lemma}

@@

The following result extends \cite[Prop.~2.28]{PaluPilaudPlamondon} to the case of locally gentle algebras.

@@

\begin{proof}
The proof of \cite[Prop.~2.28]{PaluPilaudPlamondon} applies here to show that each walk in the non-kissing facet~$F$ has at most one distinguished arrow in each direction.
Lemma~\ref{lem:ExistenceOfDistinguishedArrows} therefore shows the first two points.
Finally, Lemma~\ref{lem:walksThroughcycles} shows the last point.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop:purity}.]
The proof follows that of~\cite[Cor.~2.29]{PaluPilaudPlamondon}.
Let~$b$ denote the number of bending walks, $s$ the number of finite straight walks, and $p$ the number of infinite straight walks in a non-kissing facet~$F$ of~$\NKC$.
Since each finite straight walk uses two blossom arrows, we have~$s = 2|Q_0|-|Q_1|$ (see Remark~\ref{rem:sizeBlossomingQuiver}).
Moreover, the infinite straight walks are just the primitive oriented cycles in~$\bar Q$.

@@

A simplicial complex is \defn{thin} if each of its codimension~$1$ faces is contained in exaclty two facets.
We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.

@@

\begin{definition}
For a multiset~$V \eqdef \{a_1, \dots, a_m\}$ of vertices of~$Q_0$, we denote by~$\multiplicityVector_V \in \R^{Q_0}$ the \defn{multiplicity vector} of~$V$, defined by
\[
\multiplicityVector_V \eqdef \sum_{i \in [m]} \b{e}_{a_i} = \sum_{a \in Q_0} |\set{i \in [m]}{a_i = a}| \, \b{e}_a.
\]
For a string~$\sigma$ of~$\bar Q$, we define~$\multiplicityVector_\sigma \eqdef \multiplicityVector_{V(\sigma)}$ where~$V(\sigma)$ is the multiset of vertices of~$\sigma$. 
\end{definition}

@@

\begin{proposition}
\label{prop:gVectorsSurface}
For a walk~$\omega$ of~$\bar Q$ and a vertex~$a \in Q_0$, the $a$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
\begin{enumerate}[(i)]
\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(a)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(a)$ of~$\dissection$. Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(a)$ form a~$\SSS$ (resp.~a~$\ZZZ$).
We note that some crossings are neither positive nor negative.
\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(a)$ of~$\dissection\dual$. Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
We note that, in this case, each crossing is either positive or negative.
\end{enumerate}
\end{proposition}

@@

\begin{proof}
For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega'}$ have opposite signs on their~$a$-th coordinate automatically kiss at~$a$.
For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.
\end{proof}
